---
title: "simpleRegress"
author: "Colton Beardsley"
date: "Fall 2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## make a simple regression model

```{r}
bears <- read.csv(file="BEARS.csv",header = TRUE)
#adjust factors to be factors
bears$SEX<- as.factor(bears$SEX)
bears$MONTH<- as.factor(bears$MONTH)
```

## Model LENGTH ~ Head length


```{r}
print("First")
HeadLen <- lm(LENGTH~HEADLEN,data=bears)
plot(LENGTH~HEADLEN,data=bears)
abline(HeadLen)
summary.lm(HeadLen)
```

Adjusted R Squared - 0.8434
Residual Standard Error - 4.235

## Chest

```{r}
print("Second")
Chest <- lm(LENGTH~CHEST,data=bears)
plot(LENGTH~CHEST,data=bears)
abline(Chest)
summary.lm(Chest)
```

Adjusted R Squared - 0.7869
Residual Standard Error - 4.939

## Neck

```{r}
print("Third")
Neck <- lm(LENGTH~NECK,data=bears)
plot(LENGTH~NECK,data=bears)
abline(Neck)
summary.lm(Neck)
```

Adjusted R Squared - 0.7476
Residual Standard Error - 5.376

## Weight

```{r}
print("Fourth")
Weight <- lm(LENGTH~WEIGHT,data=bears)
plot(LENGTH~WEIGHT,data=bears)
abline(Weight)
summary.lm(Weight)
```

Adjusted R Squared - 0.7423
Residual Standard Error - 5.432

## Headwth

```{r}
print("Fifth")
HeadWth <- lm(LENGTH~HEADWTH,data=bears)
plot(LENGTH~HEADWTH,data=bears)
abline(HeadWth)
summary.lm(HeadWth)
```

Adjusted R Squared - 0.5321
Residual Standard Error - 7.23

## Age
```{r}
print("Sixth")
Age <- lm(LENGTH~AGE,data=bears)
plot(LENGTH~AGE,data=bears)
abline(Age)
summary.lm(Age)
```

Adjusted R Squared - 0.5073
Residual Standard Error - 7.511

## Concluions from data above

The linear regression models for each of the numerical variables are placed above in order with the best correlation.

We tested the residual standard error with the understanding that a lower value is better as well as compared it to the adjusted R-Squared value which we wanted as close to one.

We see that the best predictor of overall length is head length for this set of data.
